Augmentation of a Historical Harpsichord Keyboard Replica for Haptic-Enabled Interaction in Museum Exhibitions

### 2025-02-03 src/article.tex
Updates from Overleaf

3D-printed baffles were installed on the PCBs to eliminate cross-talk between adjacent sensors, as per Figure \ref{fig:baffles}. These baffles, fabricated from dark-pigmented PLA, ensured that infrared reflections from neighbouring jacks did not interfere with sensor readings. A manual visual check of plotted all sensors readings confirmed that interference from neighbouring jacks had been eliminated. RGB LEDs are placed on the reverse side of the PCB, vertically in-line with the sensors, and were added to provide a programmable means of providing visual feedback. The LEDs are controlled via a pulse width modulation (PWM) signal and are addressable individually.

\begin{figure}[!b] 
  \centering
  \includegraphics[width=\linewidth,trim={0 10cm 0 7cm},clip]{src/images/sensor-board-reverse-side-anon.png} 
  \caption{Reverse side of sensor board showing the RGB LEDs and terminal connection.}
  \Description{} 
  \label{fig:sensor-reverse}
\end{figure}

>>>>

3D-printed baffles were installed on the PCBs to eliminate cross-talk between adjacent sensors, as per Figure \ref{fig:baffles}. These baffles, fabricated from dark-pigmented PLA, ensured that infrared reflections from neighbouring jacks did not interfere with sensor readings. A manual visual check of plotted all sensors readings confirmed that interference from neighbouring jacks had been eliminated. RGB LEDs are placed on the reverse side of the PCB, vertically in-line with the sensors, and were added to provide a programmable means of providing visual feedback. The LEDs are controlled via a pulse width modulation (PWM) signal and are addressable individually.
The output signal of the multiplexer is taken from each PCB and routed to a separate ADC channel of the Arduino. Multiplexer channel select and LED PWM signals are daisy-chained through each PCB (Figure \ref{fig:sensor-reverse}).

\begin{figure}[!b] 
  \centering
  \includegraphics[width=\linewidth]{src/images/sensor-board-reverse-side-anon.png} 
  \caption{Reverse side of the sensor board showing the RGB LEDs and terminal connections. The \texttt{SIG} terminal (Top Left) is routed to an ADC channel. Power \texttt{5V, 3V, GND}, multiplexer channels \texttt{A, B, C} and LED PWM input \texttt{DI} and output \texttt{DO}  connect from the previous sensor board (Left) and are routed to the next (Right).}
  \Description{} 
  \label{fig:sensor-reverse}
\end{figure}
